Constructing Sailing Match Race Schedules: Round Robin Pairing Lists

### 2015-03-25 paper.tex
Bring skipper constraints together

\begin{figure}
\setlength{\mathindent}{0pt}\setlength{\abovedisplayskip}{0pt}\setlength{\belowdisplayskip}{0pt}
\begin{framed}
\begin{align}
    &\forall \tau \in \{0 \nldots t-1\}: \timeSlot[{\tau}] \in \{-2 \nldots t-1\} \setminus \{\sigma\} \label{var:timeSlot} \tag{V1} \\
    &\forall i \in \{0 \nldots f-1\}: \state[{i}] \in \{\FIRST,\MID,\LAST,\BYE,\END\} \label{var:state} \tag{V2} \\
    &\forall i \in \{0 \nldots f\}: \label{C1} \tag{C1} \\
    &\begin{alignedat}{3}
    &\hspace*{1em} \state[{i}] = \FIRST &\ &\Leftrightarrow&&\ \timeSlot[{i \cdot m}] \geq 0 \\
    &\hspace*{1em} \state[{i}] = \MID   &\ &\Leftrightarrow&&\ \exists j \in \{i\cdot m+1 \nldots i \cdot m+m-2\} : \timeSlot[{j}] \geq 0 \\
    &\hspace*{1em} \state[{i}] = \LAST  &\ &\Leftrightarrow&&\ \timeSlot[{(i+1)m - 1}] \geq 0 \\
    &\hspace*{1em} \state[{i}] = \BYE   &\ &\Leftrightarrow&&\ \forall j \in \{i \cdot m \nldots m \cdot (i+1)-1\} : \timeSlot[j] = -1 \\
    &\hspace*{1em} \state[{i}] = \END   &\ &\Leftrightarrow&&\ \forall j \in \{i \cdot m \nldots m \cdot (i+1)-1\} : \timeSlot[j] = -2
    \end{alignedat} \nonumber \\
&\eachOccursExactlyOnce(\timeSlot, \{0, \nldots, n-1\} \setminus \{\sigma\}) \label{C2} \tag{C2} \\
&\validStateSequence(\state) \label{C3} \tag{C3}
\end{align}
\end{framed}
\caption{A skipper-oriented model. A copy of these variables and constraints is
created for each skipper $\sigma$. The number of skippers is $n$, and $m$ is
the number of matches in a flight. The number of flights is $f = \lceil
n(n-1)/m  \rceil$, and there are $t = n(n-1)/2$ matches in total.}\label{model:skipper}
\end{figure}

@@

A boat change occurs when a skipper has been in a $\BYE$ state in flight $i$
and then is in a match in the next flight $i+1$. This is encoded using the
array of zero/one variables \ref{eq10}, and the constraint (\ref{eq11}), and
accumulated into $\totalChanges$ (\ref{eq12}).

\begin{flalign}
    & \forall_{i \in [0..f-2]} ~ \change[{i}] \in \{0,1\} \label{eq10} \\
    & \forall_{i \in [0..f-2]} ~ \change[{i}] = 1 \iff \state[{i}] = \BYE \wedge \state[{i+1}] \neq \BYE \label{eq11} \\
    & \totalChanges = \sum_{i=0}^{f-2} ~ \change[{i}] \label{eq12}
\end{flalign}

>>>>

\begin{figure}[p]
\setlength{\mathindent}{0pt}\setlength{\abovedisplayskip}{0pt}\setlength{\belowdisplayskip}{0pt}
\begin{framed}
\begin{align}
    &\forall \tau \in \{0 \nldots t-1\}: \timeSlot[{\tau}] \in \{-2 \nldots t-1\} \setminus \{\sigma\} \label{var:timeSlot} \tag{V1} \\
    &\forall i \in \{0 \nldots f-1\}: \state[{i}] \in \{\FIRST,\MID,\LAST,\BYE,\END\} \label{var:state} \tag{V2} \\
    \noalign{\smallskip \nonumber}
    &\forall i \in \{0 \nldots f\}: \label{C1} \tag{C1} \\
    &\begin{alignedat}{3}
    &\hspace*{1em} \state[{i}] = \FIRST &\ &\Leftrightarrow&&\ \timeSlot[{i \cdot m}] \geq 0 \\
    &\hspace*{1em} \state[{i}] = \MID   &\ &\Leftrightarrow&&\ \exists j \in \{i\cdot m+1 \nldots i \cdot m+m-2\} : \timeSlot[{j}] \geq 0 \\
    &\hspace*{1em} \state[{i}] = \LAST  &\ &\Leftrightarrow&&\ \timeSlot[{(i+1)m - 1}] \geq 0 \\
    &\hspace*{1em} \state[{i}] = \BYE   &\ &\Leftrightarrow&&\ \forall j \in \{i \cdot m \nldots m \cdot (i+1)-1\} : \timeSlot[j] = -1 \\
    &\hspace*{1em} \state[{i}] = \END   &\ &\Leftrightarrow&&\ \forall j \in \{i \cdot m \nldots m \cdot (i+1)-1\} : \timeSlot[j] = -2
    \end{alignedat} \nonumber \\
    &\eachOccursExactlyOnce(\timeSlot, \{0, \nldots, n-1\} \setminus \{\sigma\}) \label{C2} \tag{C2} \\
    &\validStateSequence(\state) \label{C3} \tag{C3} \\
    \noalign{\bigskip \nonumber}
    & \forall i \in \{0 \nldots f-2\}: \change[{i}] \in \{0,1\} \label{V3} \tag{V3} \\
    & \totalChanges \in \mathbb{N} \label{V4} \tag{V4} \\
    \noalign{\smallskip \nonumber}
    & \forall i \in \{0 \nldots f-2\}: \change[{i}] = 1 \Leftrightarrow \state[{i}] = \BYE \wedge \state[{i+1}] \neq \BYE \label {C4} \tag{C4} \\
    & \totalChanges = \textstyle\sum_{i=0}^{f-2} \change[{i}] \label{C5} \tag{C5}
\end{align}
\end{framed}
\caption{A skipper-oriented model. A copy of these variables and constraints is
created for each skipper $\sigma$. The number of skippers is $n$, and $m$ is
the number of matches in a flight. The number of flights is $f = \lceil
n(n-1)/m  \rceil$, and there are $t = n(n-1)/2$ matches in total.}\label{model:skipper}
\end{figure}

@@

A boat change occurs when a skipper has been in a $\BYE$ state in flight $i$
and then is in a match in the next flight $i+1$. This is encoded using the
array of zero/one variables \eqref{V3}, and the constraint \eqref{C4}, and
accumulated into $\totalChanges$ (\ref{V4},~\ref{C5}).
